The proposed work will be organized in three work packages,
corresponding to the directions described above.  Because in this
project evaluation is essentially a core thrust of the project itself,
we describe evaluation as part of the work plan.

\subsubsection{Work Package 1 (WP1)}

This work package will develop the principles and extensions to \framac for automatic translation of networks of timed automata into \acsl and ghost code, as described in the first research thrust in Section~\ref{sec:ta2framac}.
WP1 consists of the following major tasks:
\begin{itemize}[labelsep=3pt,leftmargin=12pt]

\item T1.1: This task will study the formal semantics of timed automaton networks defined in \uppaal and \prism, and define an appropriate set of the timed automaton semantics considered in this project.  The semantics would be rich enough for modeling the application systems considered in the project, specifically in WP3, while simple enough for the translation into annotations usable by static analysis tools (\framac) and dynamic analysis tools (\deepstate).  As such, there will be close collaboration and iterative design steps between this task and the other work packages. %WP3 (Application).

\item T1.2: This task will develop several methods for automatic translation of timed automaton networks into \acsl annotations and/or ghost code.  Depending on the target usage, whether for statis analysis or dynamic analysis or being inspected by programmers, a suitable method will be developed.

\item T1.3: In this task, we will implement the methods developed in T1.2 as \framac plugins.  The developed tools will be tested on the case study application in WP3, whose results will inform the tool development process.
\end{itemize}

One Ph.D. student will be needed to conduct the work in this work package, which will last for the entire duration of the project.
The student will collaborate closely with students in WP2 and WP3, and
will partially participate in the application in WP3.

\paragraph{Evaluation:} Evaluation of
Work Package 1 will be determined by the set of timed automata
networks that can be translated into \acsl and ghost code, and the
ability to use that code to prove properties.  We will use benchmark
examples (realistic code found on GitHub or in embedded systems
textbooks) to some extent, and simple test cases for constructs, but
primarily rely on the SEGA protocol and implementation code to ensure
that our efforts are successful.


\subsubsection{Work Package 2 (WP2)}

This work package will develop methods and tools to automatically translate \acsl-annotated code in \framac into a \deepstate test harness, as described in the second research thrust in Section~\ref{sec:framac2deepstate}.
WP2 is further divided into the following tasks:
\begin{itemize}[labelsep=3pt,leftmargin=12pt]
\item T2.1: This task will extend the \eacsl semantics and optimize the implementation of symbolic execution and fuzzing, so that \acsl annotations generated from timed automaton networks (in WP1) can be used in DeepState to test implementation code.
\item T2.2: This task will develop methods to translate annotations and ghost code generated for static analysis in WP1 to test specifications in \deepstate.  It will be carried out concurrently with tasks T1.1 and T1.2 in WP1, and will inform the design and method development in those tasks.
\item T2.3: In this task, we will implement the methods developed in T2.1 as extensions to \deepstate.  The tools will be applied to the case study in WP3, whose results will inform the development of the tools.
\end{itemize}

The execution of this work package will span the entire duration of the project.
One Ph.D. student will work on the tasks in WP2, and collaborate with
the students in WP1 and WP3.

\paragraph{Evaluation:} Evaluation of
Work Package 2 will be determined by the successful generation of
DeepState harnesses for \acsl annotated code, and the successful
application of those harnesses to generate tests for realistic
systems.  We will again use benchmarks and simple examples to some
extent, but primarily rely on our connection to the large, real-world
SEGA project.  In the case of test generation, in addition to faults
detected, we will use code coverage and other standard benchmarks,
including methods proposed for evaluating fuzzers in high quality
research \cite{FuzzerHicks}.


\subsubsection{Work Package 3 (WP3)}

This work package will focus on the application described in Section~\ref{sec:case-study}, as both a way to inform the methodology and tool developments in the other work packages and a case study to validate our methods and tools.
WP3 is divided into two tasks:
\begin{itemize}[labelsep=3pt,leftmargin=12pt]
\item T3.1: In this task, the existing application system will by
  studied thoroughly to extract the key requirments and
  characteristics of the embedded system implementation.  Timed
  automaton models of the communication protocol used in the system,
  at different levels of abstraction, will be developed and formally
  verified in \uppaal and/or \prism. The system information and models
  resulted from this task will inform the semantics design and method
  developments in WP1 and WP2. As time allows, and pending results
  with communication protocol, we will extend this to include sensing
  and control elements of SEGA.
\item T3.2: This task will apply the tools developed in WP1 and WP2 to the application system, in order to detect and fix bugs in the current implementation that cause the intermittent failures mentioned in Section~\ref{sec:case-study}.  It will also provide feedback to the other work packages to refine and improve the tools developed in this project.
\end{itemize}

As the tasks in this work package are conducted in tandem with WP1 and WP2, to form an informative feedback loop with the developments in other work packages, it will last for the entire duration of the project.
We expect that a group of undergraduate students, in collaboration with the Ph.D. students in WP1 and WP2, will do the tasks in this work package.

\paragraph{Evaluation:} In essence, this task \emph{is} the evaluation
aspect of our project, which forms one of the three major thrusts of
the project.  The successful application of WP1 and WP2 tools to SEGA is
essentially the driving factor in determining our success in the
project, and the key feedback to drive changes to our research
priorities or technical choices.  The measure of ``successful
application'' is (1) faults detected and corrected (2) functionality
proven correct in \framac and (3) coverage and other standard measures
of generated tests.


\subsubsection{Timeline}
\label{sec:time-line}

The project will be organized in three phases.
In the first phase, T3.1 will be conducted along with T1.1 and T2.1, and will inform the development in these tasks.
In the second phase, the focus will be on the development of translation methods in T1.2 and T2.2.
In the last phase, software tools will be developed (tasks T1.3 and T2.3) and applied to the case study (task T3.2), whose results and feedback will help refine the developed tools.
It is important that the tasks of the work packages are carried out in tandem and in close collaboration.
The timeline of the tasks will be structured as shown in Figure~\ref{fig:project-schedule}.

\begin{figure}[!tp]
  \centering
  \resizebox{.6\textwidth}{!}{%
  \begin{ganttchart}[%Specs
    hgrid style/.style={black, dotted},
    vgrid, %={*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, dashed},
      %*2{black,dotted}, *1{black, solid}},
    x unit=3mm,
    y unit chart=7mm,
    y unit title=5mm,
    %time slot format=isodate,
    title height=1,
    milestone label font=\footnotesize,
    group label font=\bfseries\footnotesize,
    title label font=\bfseries\footnotesize,
    link/.style={->, thick},
    %bar/.style={fill=blue},
    %bar height=0.7,
    %group right shift=0,
    %group top shift=0.7,
    %group height=.3,
    %group peaks width={0.2},
    %inline
    ]{1}{36}
    % labels
    % \gantttitle{A two-years project}{24}\\  % title 1 
    \gantttitle[]{Year 1}{12}                 % title 1
    \gantttitle[]{Year 2}{12}
    \gantttitle[]{Year 3}{12} \\
    \gantttitle{Q1}{3}                      % title 3
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3}
    \gantttitle{Q4}{3}
    \gantttitle{Q1}{3}
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3}
    \gantttitle{Q4}{3}
    \gantttitle{Q1}{3}
    \gantttitle{Q2}{3}
    \gantttitle{Q3}{3} 
    \gantttitle{Q4}{3}\\    

    % \ganttgroup[inline=false]{Group 1}{1}{5}\\ 
    % \ganttbar[progress=10,inline=false]{Planning}{1}{4}\\
    % \ganttmilestone[inline=false]{Milestone 1}{9} \\

    % \ganttgroup[inline=false]{Group 2}{6}{12} \\ 
    % \ganttbar[progress=2,inline=false]{test1}{10}{19} \\
    % \ganttmilestone[inline=false]{Milestone 2}{17} \\
    % \ganttbar[progress=5,inline=false]{test2}{11}{20} \\
    % \ganttmilestone[inline=false]{Milestone 3}{22} \\       

    % \ganttgroup[inline=false]{Group 3}{13}{24} \\ 
    % \ganttbar[progress=90,inline=false]{Task A}{13}{15} \\ 
    % \ganttbar[progress=50,inline=false, bar progress label node/.append style={below left= 10pt and 7pt}]{Task B}{13}{24} \\ \\
    % \ganttbar[progress=30,inline=false]{Task C}{15}{16}\\ 
    % \ganttbar[progress=70,inline=false]{Task D}{18}{20} \\ 

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP1}{1}{36}\\ [grid]
    \ganttbluebar[
        name=T11
    ]{T1.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T12
    ]{T1.2}{7}{24}\\ [grid]
    \ganttbluebar[
        name=T13
    ]{T1.3}{25}{36}\\ [grid]
    % \ganttlinkedbluebar{}{2014-10-7}{2014-10-10}
    % \ganttlinkedbluebar{}{2014-10-14}{2014-10-15}
    % \ganttlinkedbluebar{}{2014-10-17}{2014-10-17}
    % \ganttlinkedbluebar[name=FMEend]{}{2014-10-21}{2014-10-24}
    % \ganttlinkedbluebar{}{2014-10-28}{2014-10-31}\\ [grid]
    % \ganttbluebar[name=Manual]{Manual}{2014-10-30}{2014-10-31}
    % \ganttlinkedbluebar{}{2014-11-4}{2014-11-7} \ganttnewline[thick, black]

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP2}{1}{36}\\ [grid]
    \ganttbluebar[
        name=T21
    ]{T2.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T22
    ]{T2.2}{7}{24}\\ [grid]
    \ganttbluebar[
        name=T23
    ]{T2.3}{25}{36}\\ [grid]

    \ganttgroup[
        group/.append style={fill=blue}
    ]{WP3}{1}{6}
    \ganttgroup[
        group/.append style={fill=blue}
    ]{}{19}{36}\\ [grid]
    \ganttbluebar[
        name=T31
    ]{T3.1}{1}{6}\\ [grid]
    \ganttbluebar[
        name=T32
    ]{T3.2}{19}{36}
        
    % %Implementing links
    % \ganttlink[link mid=0.75]{Documentation}{FME}
    % \ganttlink{FMETutorial}{FME}
  \end{ganttchart}}
\caption{Project schedule.}
\label{fig:project-schedule}
\end{figure}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
